Mahotas: Open source software for scriptable computer vision

### 2012-08-20 paper.tex
MIN A note about numpy
This is one thing to emphacise: using Python, we build on other
structures, instead of defining our own.

Mahotas is a computer vision library for the Python. It operates on numpy arrays,
but its inner loops are implemented in \cpp{} for speed and ease of
implementation.

>>>>

Mahotas is a computer vision library for the Python. It operates on numpy
arrays~\cite{numpy}. Therefore, it uses all the infrastructure built by that
project for storing information. However, its inner loops are implemented in
\cpp{} for speed and ease of implementation.
